The Astropy Project

### 2017-12-11 main.tex
guide the colors
tighten up benchmark statements

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools.
This figure shows, for example, that \astropy, Kapteyn, and PyTPM agree
perfectly (light colors, small differences), while PALpy, pySLALIB, and PyAST
also agree perfectly amongst themselves.
However, there is an offset of around 0.2\arcsec\space with the former three
packages.
Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the accuracy values of the FK4 to Galactic
    transformation between the different packages. Each comparison block shows
    four squares representing the median, mean, maximum and standard deviation
    going from left to right and bottom to top.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}

>>>>

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools.
This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
sub-milliarcsecond differences (light colors, small differences), while PALpy,
pySLALIB, and PyAST also agree amongst themselves.
However, there is an offset of around 0.2\arcsec\space between the two groups.
Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
colors, large differences).
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the accuracy values of the FK4 to Galactic
    transformation between the different packages. Each comparison block shows
    four squares representing the median, mean, maximum and standard deviation
    going from left to right and bottom to top.
    Darker colors (larger differences) are more significant disagreements.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}
